Individual_Pop_Analysis

### 2021-10-01 IndividualPops/CMPSubpop.Rmd
added code to export dataframe from seurat assay slots

```{r}
xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))) %in% probe.list, ])
head(xprsn.mtx[1:5, 1:5])
```
```{r}
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
```
```{r}
write.table(biomark.export, file = paste0(projectName, "_Counts-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
```

>>>>

```{r}
setdiff(probe.list, rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))))
setdiff(c("Kit", "Il3ra"), rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))))

```{r}
xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))) %in% probe.list, ])
colnames(xprsn.mtx)[colnames(xprsn.mtx) == "Cd117"] <- "Kit"
colnames(xprsn.mtx)[colnames(xprsn.mtx) == "Cd123"] <- "Il3ra"
head(xprsn.mtx[1:5, 1:5])
```
```{r}
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
```
```{r}
write.table(biomark.export, file = paste0(projectName, "_Counts-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
```

### 2021-10-01 IndividualPops/Individual_SubpopAnalyses.Rmd
added code to export dataframe from seurat assay slots

## Set global variables
```{r}
pop.id <- "GMP"
folder.appendix <- "m"
fav.var <- 80
object.res <- ".1"
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
```

```{r}
folder.id <- paste0(pop.id, folder.appendix)
projectName <- paste0(pop.id, "Subpop")
```

@@

# Export for Biomark
## Import biomark probe list
```{r}
seurat.object <- readRDS(paste0(projectName, "_pctVar", fav.var, ".RDS"))
```

```{r}
probe.list <- read.table("/Users/heustonef/Desktop/10XGenomicsData/BioMark/BiomarkRNAs.txt", header = FALSE)
probe.list <- unlist(as.list(probe.list), use.names = FALSE)
```

```{r}
xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))) %in% probe.list, ])
head(xprsn.mtx[1:5, 1:5])
```
```{r}
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
```
```{r}
write.table(biomark.export, file = paste0(projectName, "_Counts-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
```

>>>>

## Set global variables
```{r}
pop.id <- "CMP"
folder.appendix <- "m2"
fav.var <- 90
object.res <- ".1"
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
folder.id <- paste0(pop.id, folder.appendix)
projectName <- paste0(pop.id, "Subpop")
```

@@

# Hierarchcial clustering
```{r}
seurat.object <- SetIdent(seurat.object, value = "RNA_snn_res.0.5")
seurat.object <- BuildClusterTree(seurat.object)
PlotClusterTree(seurat.object, direction = "downwards")
```

# Export for Biomark
## Import biomark probe list
```{r}
seurat.object <- readRDS(paste0(projectName, "_pctVar", fav.var, ".RDS"))
seurat.object <- SetIdent(seurat.object, value = paste0("RNA_snn_res", object.res))
```

```{r}
probe.list <- read.table("/Users/heustonef/Desktop/10XGenomicsData/BioMark/BiomarkRNAs.txt", header = FALSE)
probe.list <- unlist(as.list(probe.list), use.names = FALSE)
probe.list <- c(probe.list, "Kit", "Il3ra")
```
## downsample
__NOTE: do I need to do the downsampling before the corrections? Probably not, because I'm exporting counts and not corrected data
```{r}
object.downsample <- subset(biomark.object, cells = sample(Cells(biomark.object), 300))
```

## generate and export counts matrix
```{r}
xprsn.mtx <- t(as.data.frame(as.matrix(GetAssayData(object.downsample, slot = "counts"))))
object.metadata <- seurat.object@meta.data[rownames(seurat.object@meta.data) %in% rownames(xprsn.mtx), ]
# biomark.export <- xprsn.mtx
biomark.export <- merge(xprsn.mtx, object.metadata[paste0("RNA_snn_res", object.res)], by = 0)
colnames(biomark.export)[colnames(biomark.export) == "Kit"] <- "Cd117"
colnames(biomark.export)[colnames(biomark.export) == "Il3ra"] <- "Cd123"
write.table(biomark.export, file = paste0(projectName, "_Counts-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)

xprsn.mtx <- t(as.data.frame(as.matrix(GetAssayData(object.downsample, slot = "data"))))
object.metadata <- seurat.object@meta.data[rownames(seurat.object@meta.data) %in% rownames(xprsn.mtx), ]
# biomark.export <- xprsn.mtx
biomark.export <- merge(xprsn.mtx, object.metadata[paste0("RNA_snn_res", object.res)], by = 0)
colnames(biomark.export)[colnames(biomark.export) == "Kit"] <- "Cd117"
colnames(biomark.export)[colnames(biomark.export) == "Il3ra"] <- "Cd123"
write.table(biomark.export, file = paste0(projectName, "_Data-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)

xprsn.mtx <- t(as.data.frame(as.matrix(GetAssayData(object.downsample, slot = "scale.data"))))
object.metadata <- seurat.object@meta.data[rownames(seurat.object@meta.data) %in% rownames(xprsn.mtx), ]
# biomark.export <- xprsn.mtx
biomark.export <- merge(xprsn.mtx, object.metadata[paste0("RNA_snn_res", object.res)], by = 0)
colnames(biomark.export)[colnames(biomark.export) == "Kit"] <- "Cd117"
colnames(biomark.export)[colnames(biomark.export) == "Il3ra"] <- "Cd123"
write.table(biomark.export, file = paste0(projectName, "_ScaleData-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
